Expected Dependency Pair Match:\\ Predicting translation quality with expected syntactic structure

### 2009-07-29 mtjournal.tex
more info on MTC, and correlations with it

\begin{abstract}
  Recent efforts aimed at improving over standard machine translation
  evaluation methods (BLEU, TER) have investigated mechanisms for
  accounting for allowable wording differences either in terms of
  syntactic structure or synonyms/paraphrases. This paper explores an
  approach for combining scores from partial syntactic dependency
  matches with standard local n-gram matches using a statistical
  parser, and taking advantage of parse probabilities in deriving
  expected scores based on the N-best parses for the hypothesized
  sentence translation.  The new scoring metric, Expected Dependency
  Pair Match (EDPM), is shown to be superior to BLEU and TER in terms
  of correlation to human judgements and as a per-document and
  per-sentence predictor of HTER, using mean subtraction to account
  for document difficulty. Further, we explore the potential benefit
  of combining the n-gram and syntactic features of EDPM with the
  alternative wording features of TERp, with experiments showing that
  there is a benefit to accounting for syntactic structure on top of
  the semantic equivalency features.
\end{abstract}
\keywords{machine translation evaluation, syntax, dependency trees}

@@

\subsection{Corpus}
\label{sec:facorpus}
For these experiments, we use LDC Multiple Translation Chinese corpus
parts 2~\cite{LDC03MTC2} and 4~\cite{LDC06MTC4}.  These corpora
include multiple human judgments of fluency and adequacy for each
sentence, with each judgment using a different human judge and a
different reference translation.  For a rough\endnote{Our segment
  count reported in section~\ref{sec:facorpus} differs from
  \inlinecite{owczarzak07labelleddepseval}, who report 16,800 segments
  over the same corpus. We find baseline correlations (BLEU$_4$ and
  TER) lower than those reported there as well, so the results
  presented here are not directly comparable with that paper, though
  we demonstrate similar gains over those baselines in essentially the
  same corpus.
} comparison with \inlinecite{owczarzak07labelleddepseval}, we treat
each judgment as a separate segment.
%
This treatment of this corpus yields 16,815 tuples of
$\langle$hypothesis, reference, fluency, adequacy$\rangle$.  In these
experiments, we extend this tuple with automatic scores derived from
$\langle$hypothesis, reference$\rangle$ and examine the
correlations\endnote{The independence of the translation segments in
  the Multiple Translation Corpus described in
  section~\ref{sec:facorpus} is questionable, since the same
  hypothesis translations are used in multiple items, but for the sake
  of methodological comparison with prior work, this strategy is
  preserved.}  between those automatic scores and the arithmetic mean
of the fluency and adequacy measures.

\subsection{Exploring decompositions}
We begin by comparing some of the simplest DPM measures to baseline
measures case-sensitive BLEU (4-grams, with add-one smoothing) and
TER.  For these first experiments, we consider only the 1-best parse
($n=1$).
\begin{table}
  \caption{Comparing $dl,lh$ to $dlh$ and baseline correlations with
    human fluency and adequacy judgments.}
  \label{tab:facorr:subgraphs}
  \begin{tabular*}{2.5in}{lr}
    \hline
    metric  &    \multicolumn{1}{c}{$|r|$} \\
    \hline
    $F[dl,lh]$ &   0.226 \\
    % # +1 smoothing
    BLEU$_4$ &   0.218 \\
    $F[dlh]$ &     0.185 \\
    TER &      0.173 \\
    \hline
  \end{tabular*}
\end{table}
In table~\ref{tab:facorr:subgraphs} we see that using the
partial-label $dl,lh$ decomposition has a better correlation with the
fluency/adequacy scores than TER or BLEU$_4$.  These results confirm,
with a PCFG, what \inlinecite{owczarzak07labelleddepseval} found with
an LFG parser: that partial-dependency matches are better correlated
with human judgments than full-dependency links.

>>>>

\begin{abstract}
  Recent efforts aimed at improving over standard machine translation
  evaluation methods (BLEU, TER) have investigated mechanisms for
  accounting for allowable wording differences either in terms of
  syntactic structure or synonyms/paraphrases. This paper explores an
  approach for combining scores from partial syntactic dependency
  matches with standard local n-gram matches using a statistical
  parser, and taking advantage of parse probabilities in deriving
  expected scores based on the N-best parses for the hypothesized
  sentence translation.  The new scoring metric, Expected Dependency
  Pair Match (EDPM), is shown to be superior to BLEU and TER in terms
  of correlation to human judgments and as a per-document and
  per-sentence predictor of HTER, using mean subtraction to account
  for document difficulty. Further, we explore the potential benefit
  of combining the n-gram and syntactic features of EDPM with the
  alternative wording features of TERp, with experiments showing that
  there is a benefit to accounting for syntactic structure on top of
  the semantic equivalency features.
\end{abstract}
\keywords{machine translation evaluation, syntax, dependency trees}

@@

\subsection{Corpus}
\label{sec:facorpus}
For these experiments, we use LDC Multiple Translation Chinese corpus
parts 2~\cite{LDC03MTC2} and 4~\cite{LDC06MTC4}, which are composed of
translations of written Chinese news stories.  These corpora
include multiple human judgments of fluency and adequacy for each
sentence, with each judgment using a different human judge and a
different reference translation.  Both fluency and adequacy
assessments are assigned on a five-point scale. For a rough\endnote{Our segment
  count reported in section~\ref{sec:facorpus} differs from
  \inlinecite{owczarzak07labelleddepseval}, who report 16,800 segments
  over the same corpus. We find baseline correlations (BLEU$_4$ and
  TER) lower than those reported there as well, so the results
  presented here are not directly comparable with that paper, though
  we demonstrate similar gains over those baselines in essentially the
  same corpus.
} comparison with \inlinecite{owczarzak07labelleddepseval}, we treat
each judgment as a separate segment.
%
This treatment of this corpus yields 16,815 tuples of
$\langle$hypothesis, reference, fluency, adequacy$\rangle$.  In these
experiments, we extend this tuple with automatic scores derived from
$\langle$hypothesis, reference$\rangle$ and examine the per-segment
correlations\endnote{The independence of the translation segments in
  the Multiple Translation Corpus described in
  section~\ref{sec:facorpus} is questionable, since the same
  hypothesis translations are used in multiple items, but for the sake
  of methodological comparison with prior work, this strategy is
  preserved.}  between those automatic scores and the arithmetic mean
of the fluency and adequacy measures.

\subsection{Exploring decompositions}
We begin by comparing some of the simplest DPM measures to baseline
measures case-sensitive BLEU (4-grams, with add-one smoothing) and
TER.  For these first experiments, we consider only the 1-best parse
($n=1$).
\begin{table}
  \caption{Comparing $dl,lh$ to $dlh$ and baseline per-segment correlations with
    human fluency and adequacy judgments.}
  \label{tab:facorr:subgraphs}
  \begin{tabular*}{2.5in}{lr}
    \hline
    metric  &    \multicolumn{1}{c}{$|r|$} \\
    \hline
    $F[dl,lh]$ &   0.226 \\
    % # +1 smoothing
    BLEU$_4$ &   0.218 \\
    $F[dlh]$ &     0.185 \\
    TER &      0.173 \\
    \hline
  \end{tabular*}
\end{table}
In table~\ref{tab:facorr:subgraphs} we see that using the
partial-label $dl,lh$ decomposition has a better per-segment correlation with the
fluency/adequacy scores than TER or BLEU$_4$.  These results confirm,
with a PCFG, what \inlinecite{owczarzak07labelleddepseval} found with
an LFG parser: that partial-dependency matches are better correlated
with human judgments than full-dependency links.
